A dynamic programming algorithm to assess the reliability of inferences from network enrichment analysis

### 2018-05-03 doc/genesetdp.tex
small edits.

@@

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/F1_score_distribuition.png}
		\end{center}
%FIXME: Do not use figure numbers in their file name, this creates havoc if you want to reorganize them later
  \caption{{\bf Score distribution of a query size of 25 genes against the Glycolysis/Gluconeogenesis pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

We note that the calibration of

@@

%\includegraphics{img/FIXME.png}
  \caption{{\bf Calibration of GeneSetDP.} We selected 10000 random sets from the investigated genome definition and calculated their $p$ values with GeneSetDP against the Glycolysis/Gluconeogenesis pathway. To test the $p$~values uniformity we plotted them against their Normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}

>>>>

\begin{abstract}
FIXME
\end{abstract}

@@

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/F1_score_distribuition.png}
		\end{center}
%FIXME: Do not use figure numbers in their file name, this creates havoc if you want to reorganize them later
  \caption{{\bf Score distribution of a query size of 25 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

We note that the calibration of GeneSetDP is slightly conservative, i.e. the calculated $p$ values are larger than expected. Meanwhile, BinoX appears strongly anti-conservative, that is, the $p$ values are much lower than expected.

@@

%\includegraphics{img/FIXME.png}
  \caption{{\bf Calibration of GeneSetDP.} We selected 10000 random sets from the investigated genome definition and calculated their $p$ values with GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their Normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}
